Estimating the replicability of psychology experiments after an initial failure to replicate

### 2024-08-09 manuscript/coverletter/collabra_response.tex
amend response

	Finally, don't you think that if students were going to commit fraud, they'd make their study work \emph{better}? Even the studies that did rescue had smaller effect sizes than the original studies.

	Finally, regarding student error: in our prior work, we have a larger sample of 176 student replication studies, and these studies found a similar rate of replication as previous studies such as RP:P (see Boyce et al 2023). If error rates were substantially different, we'd expect lower replication.

>>>>

Finally, we think that if students were going to commit fraud, they would likely fraudulently cause their study succeed. We didn't observe this pattern, however. Even the studies that did have successful rescues had smaller effect sizes than the original studies.

Regarding student error: in our prior work, we have a larger sample of $\sim$175 student replication studies, and these studies found a similar rate of replication as previous studies such as RP:P (see Boyce et al 2023). If error rates were substantially different for students, we'd expect this to have manifested itself as lower replication rates, which we didn't observe in that study. There are many other differences between our work and RPP, but numerically we see a higher replication rate than RPP rather than the reverse, so error is unlikely to be a major determinant of student replication failure.
